Forecasting the 2024 U.S. Presidential Election

### 2024-11-03 paper/paper.qmd
Typo.
Wrong election date, updated.

The 2024 U.S. Presidential Election, which will come to an end on Nov 4, 2024, draws the worldwide attention. Especially after Joe Biden dropped out, this cycle’s election is full of more uncertainties. Predicting the electoral result is crucial and meaningful for understanding potential shifts in voter behavior, with significant implications for future leadership and policy directions in the United States.
Forecasting the election’s outcome becomes essential and meaningful for understanding potential shifts in the voters’ behavior. To make the prediction feasible, polling data becomes a primary tool for measuring voters’ sentiment and their expectations. 
This paper focuses on forecasting the electoral outcomes between Kamala Harris and Donald Trump in the 2024 cycle. Using the multiple linear regression model build on the polling data from @fivethirty, we construct an analysis by incorporating factors such as poll quality, transparency, sample size, state preference, and poll timing. By integrating these variables, the model produces a detailed forecast that accounts for regional differences and methodological variations, offering a thorough view of projected support for each candidate.
The result indicates a competitive election landscape, with Harris showing strong prospects in key swing states, while Trump retains support in traditional Republican states. These findings demonstrate how the persistent influence of geographic voting patterns and the importance of polling methodology would influence the electoral votes. 
This paper offers valuable analysis for political analysts, campaign strategists, and the public, enhancing the understanding of how polling data can inform electoral outcome predictions. However, recent election cycles have also revealed limitations in polling accuracy due to biases, non-response errors, and variations in poll quality. This study proposes a feasible model that addresses these issues to improve the reliability of election forecasts, and the uncertainty beyond the data has also been acknowledged in this paper.
The paper is organized as follows: @sec-data describes the dataset and the processing steps for model preparation. @sec-model explains the modeling approach, including predictor selection and the regression model structure. @sec-results presents the primary findings, detailing state-by-state predictions and overall electoral projections. @sec-discussion discusses the key findings, regional voting patterns, polling uncertainty and weakness. The @sec-Appendix1 provides the evaluation of the survey USA and @sec-Appendix2 discusses about the idealized methodology on survey. Besides, model diagnostics and summary are also attached in @sec-model.

@@

# Model {#sec-model}

>>>>

The 2024 U.S. Presidential Election, which will come to an end on Nov 5, 2024, draws the worldwide attention. Especially after Joe Biden dropped out, this cycle’s election is full of more uncertainties. Predicting the electoral result is crucial and meaningful for understanding potential shifts in voter behavior, with significant implications for future leadership and policy directions in the United States.
Forecasting the election’s outcome becomes essential and meaningful for understanding potential shifts in the voters’ behavior. To make the prediction feasible, polling data becomes a primary tool for measuring voters’ sentiment and their expectations. 
This paper focuses on forecasting the electoral outcomes between Kamala Harris and Donald Trump in the 2024 cycle. Using the multiple linear regression model build on the polling data from @fivethirty, we construct an analysis by incorporating factors such as poll quality, transparency, sample size, state preference, and poll timing. By integrating these variables, the model produces a detailed forecast that accounts for regional differences and methodological variations, offering a thorough view of projected support for each candidate.
The result indicates a competitive election landscape, with Harris showing strong prospects in key swing states, while Trump retains support in traditional Republican states. These findings demonstrate how the persistent influence of geographic voting patterns and the importance of polling methodology would influence the electoral votes. 
This paper offers valuable analysis for political analysts, campaign strategists, and the public, enhancing the understanding of how polling data can inform electoral outcome predictions. However, recent election cycles have also revealed limitations in polling accuracy due to biases, non-response errors, and variations in poll quality. This study proposes a feasible model that addresses these issues to improve the reliability of election forecasts, and the uncertainty beyond the data has also been acknowledged in this paper.
The paper is organized as follows: @sec-data describes the dataset and the processing steps for model preparation. @sec-modelsetup explains the modeling approach, including predictor selection and the regression model structure. @sec-results presents the primary findings, detailing state-by-state predictions and overall electoral projections. @sec-discussion discusses the key findings, regional voting patterns, polling uncertainty and weakness. The @sec-Appendix1 provides the evaluation of the survey USA and @sec-Appendix2 discusses about the idealized methodology on survey. Besides, model diagnostics and summary are also attached in @sec-model.

@@

# Model {#sec-modelsetup}
